Modeling Galaxy Spectral Energy Distributions in the SDSS Spectroscopic Survey

### 2002-02-14 docs/paper/paper.tex
lots
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@38 75dff457-8751-0410-ab1a-cd701654ce6b

These reconstructed spectra do an excellent job of reproducing the
observed galaxy fluxes. Figure \ref{k_model_plot} shows the
differences between the observed and reconstructed fluxes as a
function of redshift and as a function of absolute magnitude (in
$\band{0.1}{r}$).  The solid lines show the median differences. The
estimates of the fluxes in $g$, $r$, $i$, and $z$ do not correlate
strongly with any of these parameters, while for $u$ there is a
5--10\% discrepancy for the most distant galaxies, in the sense that
the model $u$-band flux is too bright. The dotted lines show the
boundaries containing 80\% of the objects surrounding the median
(roughly the $1.3\sigma$ limits if the distribution were
Gaussian). For $g$, $r$, and $i$, the scatter is very small ---
certainly comparable to the errors in calibration --- and roughly
independent of redshift and absolute magnitude. For $z$, the scatter
is somewhat larger, perhaps reflecting the poor signal-to-noise in
$z$, but remains constant with redshift. For $u$, the scatter is
larger, perhaps reflecting the fact that four templates simply is not
enough to characterize galaxy SEDs simultaneously in the optical and
near ultra-violet. After all, galaxies are known to have large
variations in their near-ultraviolet properties (because it depends
strongly on dust content and recent star-formation). This effect may
become more important with redshift as $u$ probes bluer and bluer
regions of the SED. All told, these spectra seem to be fair estimates
of the true underlying spectra.

An important test of the reasonableness of the fits is to check that
for a fixed type of galaxy, the distribution of the SED fits
depends little on redshift. We must be careful in performing this
check that we are comparing Figures \ref{coeffs1}--\ref{coeffs4}
demonstrates this to be the case for galaxies in several luminosity
ranges. The left column of Figure \ref{coeffs1} shows the three
coefficient ratios $a_i/a_0$ for each galaxy as a function of
redshift. The right column shows the distribution of these coefficient
ratios for two redshift ranges, showing that they are nearly
consistent. The resulting change in the color distribution inferred
from these coefficients is similarly small, at the level of what one
would expect intrinsic evolution to cause.

>>>>

These reconstructed spectra do an excellent job of reproducing the
observed galaxy fluxes. Figure \ref{k_model_plot} shows the
differences between the observed and reconstructed fluxes as a
function of redshift. There are no systematic trends with redshift,
and the standard deviations of the differences between the observed
and the reconstructed fluxes (shown on the right bottom corner of each
panel) are of order the photometric errors in the sample. This
agreement should not be overly surprising given that we have five
galaxy fluxes and four templates to fit, and when one considers the
fact that galaxy colors are known to be correlated with one another.

An important test of the reasonableness of the fits is to check that
for a fixed type of galaxy, the distribution of the fixed frame colors
depends little on redshift. Because the galaxies shown in Figures
\ref{k_coeffdist_plot} and \ref{k_model_plot} are inhomogeneously
selected --- some are Main Sample

We must be careful in performing this check that
we are comparing Figures \ref{coeffs1}--\ref{coeffs4} demonstrates
this to be the case for galaxies in several luminosity ranges. The
left column of Figure \ref{coeffs1} shows the three coefficient ratios
$a_i/a_0$ for each galaxy as a function of redshift. The right column
shows the distribution of these coefficient ratios for two redshift
ranges, showing that they are nearly consistent. The resulting change
in the color distribution inferred from these coefficients is
similarly small, at the level of what one would expect intrinsic
evolution to cause.
